Coherent optical creation of a single molecule

### 2020-11-30 paper.tex
Remove out of date note about detuning
Non sense... I don't care anymore

\begin{abstract}
  We report on coherent association
  of atoms into a single weakly bound NaCs molecule in an optical tweezer
  through an optical Raman transition.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69\mathrm{\%}$.
  The molecules have a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.83(2)~\mathrm{G}$
  and are created with higher than $60\mathrm{\%}$ probability in the motional ground state.
  This technique does not rely on Feshbach resonances or narrow excited-state lines
  and may allow a wide range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

We choose the tweezer frequency to be $288560~\mathrm{GHz}$
which is far detuned (by $\approx\!145~\mathrm{GHz}$) from the $v' = 0$ line.
Guided by the coupled-channel calculations,
we locate the Raman resonance for the atoms-to-molecule transition at
$770.57150(9) ~\mathrm{MHz}$ with about $3.75~\mathrm{mW}$ tweezer power
focused down to a waist of $ 0.9~\mathrm{\mu m}$, as shown in Fig.~\ref{f-raman}a.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$.
% The background level of $31~\mathrm{\%}$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step,
so successful transfer of the atoms to the molecular state is detected as loss of atoms.
We observe a Fourier-limited linewidth, which is evidence of a coherent transfer.
In order to verify the coherence of the transfer directly,
we fix the two-photon detuning on resonance and scan the pulse time.
Fig.~\ref{f-raman}b shows the observed coherent Rabi oscillation between the atomic and molecular states.
Fitting the data with a decaying Rabi oscillation suggests that
$69~\mathrm{\%}$ of atoms initially in the motional ground state are transferred into the molecular state after a $\pi$ pulse.
This transfer efficiency is limited mainly by the molecular lifetime,
which can be measured directly by preparing the molecule with a $\pi $ pulse
and then using a second $\pi$ pulse to dissociate the molecule back to atoms
after a variable wait time.
The result in Fig.~\ref{f-lifetime}a shows a molecular lifetime of $0.199(9)~\mathrm{ms}$
consistent with the decay of the Rabi oscillation.
We obtain the Raman Rabi frequency by fitting our measurements to a model
that includes a Raman Rabi frequency and
a finite lifetime for the molecular state, as shown in Fig.~\ref{f-raman}a and b.
We account for the small effect of atomic state loss by measuring the one-body and
two-body lifetime of the atoms directly without turning on the second frequency,
as shown in Fig.~\ref{f-lifetime}b.
The fit including all these effects gives a Raman Rabi frequency
of $2\pi\times3.28(4)~\mathrm{kHz}$.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6~\mathrm{GHz}$.
    (a) The light shift of the Raman resonance fitted to
    $(f_{R0}+a\cdot P+b\cdot P^2)+c\cdot P/\Delta$
    where $P$ is the power in the tweezer,
    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweer}}$ is the detuning from
    the PA resonance frequency $f_{\mathrm{PA}0}$.
    The small $P^2$ term included in the fit is caused by the effective magnetic field
    generated by the tweezer, which is perpendicular to the real magnetic field.
    The fitting results are $f_{\mathrm{PA}0}=288711~\mathrm{GHz}$,
    $f_{R0}=770.20052(2)~\mathrm{MHz}$, $a=8.78(7)~\mathrm{kHz/mW}$,
    $b=-3.186(9)~\mathrm{kHz/mW^2}$
    and $c=16.43(2)~\mathrm{MHz\cdot GHz/mW}$.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to $(a + b/\Delta)\cdot P^{1.29}$.
    The detuning is calculated using the PA frequency fitted in (a).
    The fitting results are $a=-2\pi\times\!0.41(2)~\mathrm{kHz/mW^{1.29}}$
    $b=4\pi^2\times\!167(2)~\mathrm{kHz\cdot\!GHz/mW^{1.29}}$.
    (c) Tweezer power dependency of light shift (top) and Raman Rabi frequency (bottom)
    on a log-log plot showing the power-law scaling.
    \label{f-det}}
\end{figure*}

First we look at the change in resonance frequency to determine $\Omega_m$.
We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
When we vary the tweezer frequency around the $v'=0$ intermediate state,
we can further observe a $1/\Delta$ component
and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is due to the coupling between the molecular state
and the $v'=0$ intermediate state.
From this measurement, we can extract a $\Omega_m$ of
$2\pi\times181.3(1)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
This number is within $50~\mathrm{\%}$
of the value $2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory.

In order to calculate the ratio $\Omega_m/\Omega_a$,
we now need to extract $ \Omega_a $.
We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power
due to the change in the atomic wavefunction caused by
tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
As discussed before, for weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
which fits well to our experimental result, as shown in Fig.~\ref{f-det}c.
Similar to the light shift, the detuning dependency of the Raman Rabi frequency
is determined by a constant background component and
a $v'=0$ component that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency at our detuning is
$2\pi\times1.15(1)~\mathrm{kHz\cdot mW^{-1.29}}$,
or $2\pi \times 6.34(8)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
$2\pi\times 5.23(6)~\mathrm{MHz}$.
This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $67.1(8)$,
which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
from the $v'=0$ state to be higher than expected.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.

\begin{table}[ht]
  \centering
  \begin{tabular}{c|c|c}
    & Experiment & Theory \\ \hline
    $\Omega_R $ & $-$ & $2\pi \times 15.3~\mathrm{kHz}$ \\
    $\Gamma_s$ & $-$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
    $\Omega_m$ & $2\pi \times 351.1(2)~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
    $\Omega_a$ & $2\pi \times 5.23(6)~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
    $\Omega_m/\Omega_a$ & $67.1(8)$ & $77.7$
  \end{tabular}
  \caption{Comparison between theory and experiment of $\Omega_R,\Gamma_s, \Omega_m, \Omega_a$. $\Omega_R$ and $ \Gamma_s $ are reported at $145~\mathrm{GHz}$ detuned from the $v' = 0$ state. All numbers are reported at $3.75$ mW tweezer power. }
  \label{tab:rabi_freqs}
\end{table}

>>>>

\begin{abstract}
  We report on coherent association
  of atoms into a single weakly bound NaCs molecule in an optical tweezer
  through an optical Raman transition.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69\mathrm{\%}$.
  The molecules have a binding energy of $770.1969(2)~\mathrm{MHz}$ at $8.83(2)~\mathrm{G}$
  and are created with higher than $60\mathrm{\%}$ probability in the motional ground state.
  This technique does not rely on Feshbach resonances or narrow excited-state lines
  and may allow a wide range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

We choose the tweezer frequency to be $288560~\mathrm{GHz}$
which is far detuned (by $\approx\!151~\mathrm{GHz}$) from the $v' = 0$ line.
Guided by the coupled-channel calculations,
we locate the Raman resonance for the atoms-to-molecule transition at
$770.57150(9) ~\mathrm{MHz}$ with about $3.75~\mathrm{mW}$ tweezer power
focused down to a waist of $ 0.9~\mathrm{\mu m}$, as shown in Fig.~\ref{f-raman}a.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$.
% The background level of $31~\mathrm{\%}$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step,
so successful transfer of the atoms to the molecular state is detected as loss of atoms.
We observe a Fourier-limited linewidth, which is evidence of a coherent transfer.
In order to verify the coherence of the transfer directly,
we fix the two-photon detuning on resonance and scan the pulse time.
Fig.~\ref{f-raman}b shows the observed coherent Rabi oscillation between the atomic and molecular states.
Fitting the data with a decaying Rabi oscillation suggests that
$69~\mathrm{\%}$ of atoms initially in the motional ground state are transferred into the molecular state after a $\pi$ pulse.
This transfer efficiency is limited mainly by the molecular lifetime,
which can be measured directly by preparing the molecule with a $\pi $ pulse
and then using a second $\pi$ pulse to dissociate the molecule back to atoms
after a variable wait time.
The result in Fig.~\ref{f-lifetime}a shows a molecular lifetime of $0.199(9)~\mathrm{ms}$
consistent with the decay of the Rabi oscillation.
We obtain the Raman Rabi frequency by fitting our measurements to a model
that includes a Raman Rabi frequency and
a finite lifetime for the molecular state, as shown in Fig.~\ref{f-raman}a and b.
We account for the small effect of atomic state loss by measuring the one-body and
two-body lifetime of the atoms directly without turning on the second frequency,
as shown in Fig.~\ref{f-lifetime}b.
The fit including all these effects gives a Raman Rabi frequency
of $2\pi\times3.28(4)~\mathrm{kHz}$.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (a) The light shift of the Raman resonance fitted to$a(P)+b(P)/\Delta$, where
    $a(P)$ and $b(P)=(\Omega_a^2-\Omega_m^2)/2$
    are tweezer power dependent background and $v'=0$ contribution
    to the light shift,
    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweer}}$ is the detuning from
    the PA resonance frequency $f_{\mathrm{PA}0}$.
    The $a(P)$s are fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
    at zero tweezer power to be $f_{R0}=770.1969(2)~\mathrm{MHz}$.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to$c(P)+d(P)/\Delta$, where
    $c(P)$ and $d(P)=\Omega_a\Omega_m/2$
    are tweezer power dependent background and $v'=0$ contribution.
    The detuning is calculated using the PA frequency fitted in (a).
    The $c(P)$s and $d(P)$s are proportional to $P^{1.29}$
    and the fit gives $c(P)/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
    and $d(P)/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz/mW^{1.29}}$.
    The fitting results for (a) and (b) are shown in table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
    $b(P)$ and $d(P)$ on a log-log scale showing the $P^{0.5}$ scaling of $\Omega_m$ and
    the $P^{0.79}$ scaling of $\Omega_a$.
    \label{f-det}}
\end{figure*}
\begin{table}[ht]
  \centering
  \begin{tabular}{|c|c|}
    $f_{\mathrm{PA}0}$&$288711.8~\mathrm{GHz}$\\\hline
    $a(0.75~\mathrm{mW})$&$770.20452(6)~\mathrm{MHz}$\\
    $b(0.75~\mathrm{mW})$&$-12.46(2)~\mathrm{MHz\cdot GHz}$\\
    $a(1.5~\mathrm{mW})$&$770.2081(1)~\mathrm{MHz}$\\
    $b(1.5~\mathrm{mW})$&$-24.44(3)~\mathrm{MHz\cdot GHz}$\\
    $a(3.75~\mathrm{mW})$&$770.1943(3)~\mathrm{MHz}$\\
    $b(3.75~\mathrm{mW})$&$-60.66(8)~\mathrm{MHz\cdot GHz}$\\\hline
    $c(0.75~\mathrm{mW})$&$-2\pi\times0.29(2)~\mathrm{kHz}$\\
    $d(0.75~\mathrm{mW})$&$-4\pi^2\times115(4)~\mathrm{kHz\cdot GHz}$\\
    $c(1.5~\mathrm{mW})$&$-2\pi\times0.63(4)~\mathrm{kHz}$\\
    $d(1.5~\mathrm{mW})$&$-4\pi^2\times275(6)~\mathrm{kHz\cdot GHz}$\\
    $c(3.75~\mathrm{mW})$&$-2\pi\times2.4(2)~\mathrm{kHz}$\\
    $d(3.75~\mathrm{mW})$&$-4\pi^2\times0.95(3)~\mathrm{MHz\cdot GHz}$\\
  \end{tabular}
  \caption{Fitting results for Fig.~\ref{f-det}(a,b).
    \label{tab:f-det:fit}}
\end{table}

First we look at the change in resonance frequency to determine $\Omega_m$.
We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
When we vary the tweezer frequency around the $v'=0$ intermediate state,
we can further observe a $1/\Delta$ component
and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is due to the coupling between the molecular state
and the $v'=0$ intermediate state.
From this measurement, we can extract a $\Omega_m$ of
$2\pi\times180.87(7)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
This number is within $40~\mathrm{\%}$
of the value $2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory.

In order to calculate the ratio $\Omega_m/\Omega_a$,
we now need to extract $ \Omega_a $.
We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power
due to the change in the atomic wavefunction caused by
tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
As discussed before, for weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
which fits well to our experimental result, as shown in Fig.~\ref{f-det}c.
Similar to the light shift, the detuning dependency of the Raman Rabi frequency
is determined by a constant background component and
a $v'=0$ component that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency at our detuning is
$2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
$2\pi\times 5.5(2)~\mathrm{MHz}$.
This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
from the $v'=0$ state to be higher than expected.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.

\begin{table}[ht]
  \centering
  \begin{tabular}{c|c|c}
    & Experiment & Theory \\ \hline
    $\Omega_R $ & $-$ & $2\pi \times 15.3~\mathrm{kHz}$ \\
    $\Gamma_s$ & $-$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
    $\Omega_m$ & $2\pi \times 348.3(3)~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
    $\Omega_a$ & $2\pi \times 5.5(2)~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
    $\Omega_m/\Omega_a$ & $63(3)$ & $77.7$
  \end{tabular}
  \caption{Comparison between theory and experiment of $\Omega_R,\Gamma_s, \Omega_m, \Omega_a$. $\Omega_R$ and $ \Gamma_s $ are reported at $151~\mathrm{GHz}$ detuned from the $v' = 0$ state. All numbers are reported at $3.75$ mW tweezer power. }
  \label{tab:rabi_freqs}
\end{table}
